### 2015-06-26 narrative/intro.tex
added more details to the opening

The Lightweight File Systems project from Sandia sought to strip down a file
system to the minimum features and encourage layering our auxiliary services to
add features for a particular use. Sirocco is the storage mechanism for LWFS.
We are proposing to combine the apps knowledge from ORNL with the SNL system
and the expertise gaps represented in the additional people to investigate how
to make a data, workflow, and application aware storage system.

>>>>

The Lightweight File Systems~\cite{lwfs} (LWFS) project from Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, are added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project demonstrated that using a core
object storage system with integrated security providing authentication and
autorization services, customized storage interfaces could be developed with
exactly the overhead required for different applications. The second phase of
LWFS, known as Sirocco~\cite{sirocco}, is investigating how to manage storage
devices for efficient and scalable storage performance.  Sirocco has been in
process for three years and has a usable storage infrastructure system. This
proposal seeks to build upon this work to demonstrate an application, data, and
usage aware storage system optimized for exascale composite applications and
capability application runs. We are proposing to combine the applications
knowledge from ORNL with the SNL LWFS system and storage system knowledge, the
metadata and storage systems knowledge of UCSC, and the middleware expertise of
Rutgers to investigate how to make a data, workflow, and application aware
storage system.
